Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2017-02-14 Experiments.tex
some comments in Experiment Design.

In this section we describe experiments that have been performed by running the ATLAS workload on TITAN's batch queue by means of the next generation executor.   
The importance of these experiments is twofold: on the one side, we illustrate the performances of the NGE; on the other side, they help to characterize TITAN's batch queue and we show that it can be used as alternative to backfilling. Since we aim to study the response time of batch queue as it is perceived by a common user,  special privileges have been asked to system administrator.
%This is particularly important for the development of future execution strategies because queue time becomes dominant in

Experiments aim to show the number of completed events as function of the time. 
Each experiment corresponds to a number of different and independent runs that is meaningful from a statistical point of view. Each run consists in the sustained execution of the ATLAS workload for a pre-determined period of time \aanote{A week? 10 days?}. Since execution of events is carried on by means NGE jobs, each run is based on a script that maintains constant pressure on TITAN's batch queue.
The main tasks of the script are to:  i) guarantee that there are constantly four NGE jobs eligible for running on TITAN's queue (note that four jobs is the maximum allowed in TITAN's batch queue \ref{}); ii)  bind Athena-MP jobs to the NGE jobs; iii) perfom garbage collection. No limit in the number of NGE jobs is imposed.

The simulation of events is due to the following execution model: the script binds a number of Athena-MP jobs that is equal to the number of nodes on which NGE job is running; then, NGE job spawns the Athena-MP jobs on the nodes; finally, the Athena-MP jobs will simulate a number of events that is proportional to the wall-time of the NGE job. As a consequence, the number of nodes determines the number of events that can be simulated concurrently whereas the wall-time determines the number of events that can be simulated one after the other. These two parameters together determine the size of the NGE job.

>>>>

In this section we describe experiments that have been performed by running the ATLAS workload on TITAN's batch queue by means of the next generation executor (NGE) \jhanote{We'll need to reference the section/sub-section where this is discussed}.

The importance \jhanote{aim?} of these experiments is twofold: on the one side, we illustrate the performances of the NGE; on the other side, they help to characterize TITAN's batch queue and we show that it can be used as alternative to backfilling. Since we aim to study the response time of batch queue as it is perceived by a common user,  special privileges have been asked to system administrator. \jhanote{I don't think the second point captures accurately why we are interested in the NGE. Please refine}

%This is particularly important for the development of future execution strategies because queue time becomes dominant in

Experiments aim to show \jhanote{calculate? determine?} the number of completed events as function of the time. 
Each experiment corresponds to a number of different and independent runs that is meaningful from a statistical point of view. \jhanote{previous sentence needs fixing} Each run consists of a sustained execution of the ATLAS workload for a pre-determined period of time \aanote{A week? 10 days?}. \jhanote{How do we determine this time window?} Since execution of events is carried on by means \jhanote{what is an NGE job?} NGE jobs, each run is based on a script that maintains constant pressure on TITAN's batch queue. \jhanote{please separate what we are trying to achieve from how..}

The main tasks of the script are to:  i) guarantee that there are constantly four NGE jobs eligible for running on TITAN's queue (note that four jobs is the maximum allowed in TITAN's batch queue \ref{}); ii)  bind Athena-MP jobs to the NGE jobs; iii) perform garbage collection. No limit in the number of NGE jobs is imposed.

The simulation of events is due to the following execution model: the script\jhanote{the script is too casual/imprecise} binds a number of Athena-MP jobs that is equal to the number of nodes on which NGE job is running; then, NGE job spawns the Athena-MP jobs on the nodes; finally, the Athena-MP jobs will simulate a number of events that is proportional to the wall-time of the NGE job. As a consequence, the number of nodes determines the number of events that can be simulated concurrently whereas the wall-time determines the number of events that can be simulated one after the other. These two parameters together determine the size of the NGE job. \jhanote{please refine. difficult to understand}
